
%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://jaronellingson.com/}{\Large Jaron Ellingson}} & Email : \href{mailto:jaringson@gmail.com}{jaringson@gmail.com}\\
  \href{http://jaronellingson.com/}{http://jaronellingson.com} & Mobile : 480-603-8723 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brigham Young University}{Provo, Utah}
      {Master of Science in Mechanical Engineering; GPA: 3.70}
      	{Aug. 2018 -- April 2020}
      \resumeItemListStart
	      \resumeItem{Relevant Classes}
		     {Linear System Theory, Control Systems, Robotic Vision, Math  of Signals and Systems, Deep Learning, Robotics, Flight Dynamics, Algorithm Design \& Analysis, Advanced Programming, Mechatronics }
      \resumeItemListEnd 
    \resumeSubheading
    {Brigham Young University}{Provo, Utah}
    {Bachelor of Science in Mechanical Engineering; Minors is Computer Science and Math; GPA: 3.89}
    {April 2018}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
	\resumeSubheading
	{MIT Lincoln Laboratory}{Lexington, MA}
	{Summer Research Intern}{June 2018 - Aug 2018}
	\resumeItemListStart
	\resumeItem{Video Classification}
	{Implemented several deep learning architecture for video classification. Long-short term memory cells, 3D nets, transfer learning, etc. }
	\resumeItem{Communication}
	{Contributed to weekly meetings and presented a final debriefing to demonstrate research and recommend appropriate future research for the laboratory. }
	\resumeItem{Innovation}
	{Took a broad topic and came up with concrete applications. }
	\resumeItem{Technology Used}
	{ Python, Tensorflow, Keras }
	\resumeItemListEnd
	
	
	\resumeSubheading
	{Brigham Young University}{Provo, Utah}
	{Research Assistant}{Aug 2016 - Present}
	\resumeItemListStart
	\resumeItem{Computer Vision Applications}
	{Developed vibrational mode shape identification software using machine learning as well as other computer vision techniques. }
	\resumeItem{Research Paper}
	{Currently writing a research paper with graduate student. Invite to present at a conference. }
	\resumeItem{Technology Used}
	{ Python, Tensorflow }
	\resumeItemListEnd
	
	\resumeSubheading
	{SpotterRF}{Orem, Utah}
	{Software Engineering Intern}{Jan 2016 - Aug 2016}
	\resumeItemListStart
	\resumeItem{Radar Testing Software}
	{Rewrote testing software to be desirable and transferable to the needs of manufacturing.}
	\resumeItem{Technology Used}
	{Python, HTML/CSS, Javascript, MongoDB, CouchDB }

\resumeItemListEnd


\resumeSubHeadingListEnd


%-----------Leadership/Projects-----------------
\section{Leadership/Projects}
  \resumeSubHeadingListStart
  
	
	  
	 
		
		\resumeSubheading{Deep Remote Control}  {Provo, Utah}{Deep Learning Flight Estimator}{July 2017 - Present}
			\resumeItemListStart
				\resumeItem{Deep Learning}
					{Researched and implemented deep learning algorithms for 3rd-person estimation and control of unmanned aerial vehicles. Used deep residual neural networks. }
				\resumeItem{Conference Paper}
					{Submitted to International Conference on Robotics and Automation (ICRA) 2019 conference}
				\resumeItem{Flight Control}
					{Implemented particle filter with both a simulation and real life testing. Submitted to International Conference on Robotics and Automation 2019 conference}
				\resumeItem{Funding Proposals}
					{Wrote proposals for getting undergraduate funding through BYU library, Office of Research and Creative Activities, etc. Outcome is to write a research paper. }
				\resumeItem{Technology Used}
					{ Tensorflow, C++, OpenCV, ROS, LaTeX }
		\resumeItemListEnd
		
		\resumeSubheading{Mars Rover University Challenge} {Provo, Utah}{Autonomous Navigation Developer}{Aug 2017 - June 2018}
			\resumeItemListStart
				\resumeItem{Visual Tracking}
					{ Researched innovative navigation and tracking software which included deep neural classification. Implemented an autonomous system onto a rover.}
				\resumeItem{Task Lead}
					{Organized efforts to make rover completely autonomous, complete with accurate rover position estimations and obstacle avoidance.}	
				\resumeItem{Technology Used}
					{ROS, Python, C++, OpenCV }
		\resumeItemListEnd
		
		 \resumeSubheading{Association for Unmanned Vehicle Systems International } {Provo, Utah}{Computer Vision Developer}{Sept 2015 - June 2017}
			 \resumeItemListStart
				 \resumeItem{Target Identification}
					 {Implemented spatial transformer deep neural network to track and classify targets for an unmanned aerial vehicle search and rescue mission.}
				 \resumeItem{Technology Used}
					 { Python, Tensorflow, C++, OpenCV, ROS }
			\resumeItemListEnd
		
	  \resumeSubHeadingListEnd





%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Generative Adversarial Networks}
      {Completed a facial generative network through the improved WGAN.}
    \resumeSubItem{Siamese Network}
      {Implemented siamese networks to quickly classify resonance frequencies for turbine blades.}
    \resumeSubItem{Residual Networks}
      {Created residual networks to classify orientation of an aircraft for 3rd-person control.}
    \resumeSubItem{Recurrent Neural Network}
      {Executed an RNN to mimic text, such as Tom Sawyer, through LSTMs and GRUs.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Python, C++, C\#, Java, SQL, Matlab, Javascript}
%      \hfill
%    }
%    \item{
%    	\textbf{Technologies}{: Tensorflow, ROS, OpenCV, GitHub, Linux }
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
